\documentclass[11 pt]{article}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{mathpazo}
\geometry{left=1in,right=1in,top=1in,bottom=1in}

\begin{document}
\newcommand{\snn}{\sqrt{s_{NN}}}
\begin{center}
Curriculum Vitae \\
{\bf Dr. Peter Alan Steinberg}\\
{\bf Senior Physicist}\\
{\bf Brookhaven National Laboratory}\\
\end{center}

\begin{tabbing}
\\
{\bf General:}\\
Name: \hspace{2cm} \= Dr. Peter Alan Steinberg \\
Address: \> Brookhaven National Laboratory\\  
        \> P.O. Box 5000\\
        \> Building 510C \\
        \> Upton, NY 11973-5000 \\
Phone: \> Office: 631-344-4390 \\
       \> Home:   917-443-7417\\
e-mail: \> peter.steinberg@bnl.gov \\
WWW: \> \url{http://cern.ch/steinber} \\
Birth: \> November 21, 1969 in Chicago, Illinois, USA \\
Nationality: \> U.S.A. \\
\\
\textbf{Employment History:}\\
12/19 - present \> Senior Scientist, BNL Physics Department\\
03/09 - 12/19 \> Physicist in PHENIX Research Group, BNL Physics Department  \\
01/07 - 3/09 \> Physicist in Heavy Ion Research Group, BNL Physics Department  \\
04/06 \> Awarded Tenure in BNL Chemistry Department\\
10/04 - 01/07 \>Physicist at Brookhaven National Laboratory, Chemistry Department\\
4/02 - 10/04\>Associate Scientist at Brookhaven National Laboratory,\\ \> Supervisor: M. Baker\\
8/02 - 2/03\> Fulbright Scholar at the University of Cape Town, South Africa, Host: J. Cleymans\\
12/99 - 4/02 \>Assistant Scientist at Brookhaven National Laboratory Chemistry Department,\\ \> PHOBOS Group, Supervisor: M. Baker\\
2/98 - 11/99 \>Post-doc at Columbia University, Nevis Labs, Supervisors: B.A. Cole\\ \> and W.A. Zajc.\\
\\
{\bf Research Interests:}\\
\> Experimental Nuclear and High-Energy Physics.\\
\> Study of terakelvin QCD matter using bulk properties and hard probes.\\
\> Study of electromagnetic processes in heavy ion collisions, ultraperipheral collisions.\\
\> Zero-degree calorimetry for centrality characterization and tagging of electromagnetic\\ \> processes.\\
\> Silicon Detectors, event building and high-level trigger systems.\\  
\> Software environments and tools for high energy physics collaborations.\\
\\
\textbf{Current Research \& Affiliations:}\\
Research Group: \> PHENIX, BNL Physics Department (Principal investigator: D. Morrison) \\
%Honorary: \> UCT-CERN Research Centre, University of Cape Town (PI: J. Cleymans)\\
Experiments: 
\> ATLAS at CERN, Spokesperson: K. Jakobs (CERN) \\
\> sPHENIX at RHIC, Spokespeople: D. Morrison (BNL), G. Roland (MIT)\\
\\
\textbf{Education:}\\
2/98 \> PhD. Received\\
\> ``Search for Disoriented Chiral Condensates in 158
AGev Pb+Pb Collisions''\\
9/93 - 1/98 \> PhD. Student in Physics at the Massachusetts Institute
of Technology\\
\>Thesis advisor - Bolek Wyslouch.\\
9/92 - 6/93 \> Physics coursework at Yale University \\
5/92 \> Completion of B.A. in Political Science at Yale University \\
9/88 - 5/92 \> Yale University, New Haven, Connecticut \\
9/74 - 5/88 \> Francis W. Parker School, Chicago, Illinois \\
\\
\textbf{Awards and Honors:}\\
9/17 \> Fellow of the APS Division of Nuclear Physics\\
7/03 - 7/06 \> Honorary Research Associate at University of Cape Town, South Africa \\
8/02 - 3/03 \> Fulbright Award for Lecturing and Research in Cape Town, South Africa\\
5/92 \> Philo S. Bennett Prize for Best Senior Essay in Political Philosophy \\
9/88 \> National Merit Scholarship \\
\\
\textbf{Responsibilities:}\\
04/19 - present \> Co-convenor, ATLAS Heavy Ion Physics ultraperipheral (UPC) subgroup\\
10/18 - present \> Project leader, ATLAS Zero Degree Calorimeter (ZDC)\\
10/16 - 10/18 \> Co-convenor, ATLAS Heavy Ion Physics Group \\
05/15 - 10/16 \> Project leader, ATLAS ZDC\\
03/15 - 03/18 \> Elected to BNL Council \\
11/14 - 10/16 \> Co-convenor of ATLAS Heavy Ion Electroweak/Quarkonia subgroup\\
10/08 - 10/11 \> Co-convenor of ATLAS Heavy Ion Physics Group\\
11/05 - 10/08 \> ATLAS-HI Computing Liaison, ATLAS-HI Global Physics Group \\
04/05 - 04/12 \> PHOBOS Computing Liaison \\
08/03 - 05/06 \> Project Manager of PHOBOS Experiment (decommissioned)\\
02/01 - 08/03 \> Head of PHOBOS Computing\\
03/00 - 01/06 \> Co-convenor of Multiplicity Physics Working Group\\
11/99 - 02/01 \> Head of PHOBOS Online Computing\\
02/98 - 11/99 \> Development and Implementation of PHENIX Event Builder\\
\\
\textbf{Organizational and editorial responsiblities:}\\
06/20\>International Organizing Committee, Hard Probes 2020, Austin, Texas (online)\\
06/19\>International Organizing	Committee, Initial Stages 2021, Rehoot, Israel\\
06/19\>co-Chair, Initial Stages 2019, New York City, USA\\
05/18\>International Organizing Committee, Quark Matter 2018, Venice, Italy\\
09/17\>International Organizing Committee, Initial Stages 2017, Krakow, Poland\\
05/16\>International Organizing Committee, Initial Stages 2016, Lisbon, Portugal\\
05/15\>International Organizing Committee, Hard Probes 2015, Montreal Canada\\
02/15\>International Organizing Committee, ICPAQGP 2015, Kolkata, India\\
12/14\>Local Organizing Committee, Initial Stages 2014, Napa, CA\\
11/13\>Local Organizing Committee, Hard Probes 2013, Cape Town, South Africa, \\
\> November 2013\\
11/12\>Co-editor of volume ``Strongly correlated quantum fluids: ultracold quantum gases,\\ \> quantum chromodynamic plasmas and holographic duality'', \\\> New Journal of Physics, Volume 14, November 2012.\\
08/12\>Local Organizing Committee, Quark Matter 2012, Washington, DC, \\ \>August 13-18, 2012\\
05/12\>International Advisory Committee, Hard Probes 2012, Calgiari, \\ \>Sardegna, May 27 - June 1, 2012\\
06/11\>Organizer of RHIC/AGS Users Meeting, June 2011\\
05/11\>International Advisory Committee, Quark Matter 2011, Annecy, France,\\ \> May 23-28, 2011\\
02/11\>Scientific Organizing Committee, Les Houches QCD 2011, Feb. 13-18, 2011\\
06/10\>Elected incoming chair of RHIC/AGS Users Executive Committee (until 6/13)\\
09/09\>Session organizer for ISMD 2009, Gomel, Belorussia, September 1-7, 2009.\\
06/09 \>Co-organizer of ``Baryon stopping \& Entropy production'' at RHIC/AGS \\ \>Users' Meeting 2009, Brookhaven National Laboratory.\\
04/09\>International Advisory Committee, Quark Matter 2009, Knoxville, TN, \\ \>March 30-April 4, 2009\\
02/09\> Co-organizer (with W.A. Zajc) of ``Quest for the Perfect Liquid: Connecting\\ \> Heavy Ions, String Theory, and Cold Atoms'', symposium at AAAS2009, \\ \>Chicago, Illinois, February 15, 2009.\\
01/09-present\> Co-editor ``RHIC News'' and ``InsideRHIC'' at Brookhaven National Laboratory\\
06/06\>Co-organizer of ``From High Energy to High $\mu_B$'', Workshop at the RHIC/AGS\\
\>Users Meeting, June 5, 2006\\
05/06\>Co-organizer of ``Boulder Workshop 2006'', UC Boulder, May 2006\\
03/05\>Co-organizer of ``Boulder Workshop 2005'', UC Boulder, March 2005\\
11/04-\>Co-organizer of ``New Directions'' Working Group in the ``RHIC II Science''\\\> Effort, with Prof. James Nagle, UC Boulder\\
09/04\>Local co-organizer of ``Strange Quark Matter 2004'', 9/10-15/2004, Cape Town,\\ 
\>South Africa.\\
05/04\>Co-organizer of ``Bulk Dynamics'' Workshop at RHIC/AGS Users Meeting, \\
\>May 10-14, 2004, BNL.\\
04/04\>Co-organizer of ``RHIC II Physics and Perspectives on a New Comprehensive\\
\>Detector'', Yale University.\\
12/03-\> Working group for a New RHIC II Detector (R2D)\\
08/03-\> Nuclear Physics Planning Group - Brookhaven National Laboratory \\
08/03-12/03\> RHIC Planning Committee - Brookhaven National Laboratory \\ 
01/01\>Local Organizing Committee and Organizer for Student Pre-Conference \\
\>Symposium, Quark Matter 2001, Stony Brook, NY.\\
\\
\textbf{Teaching Experience}\\
3/03 - 5/03\>Honours Module on Particle Physics (textbook: D.H. Perkins)\\
2/03 - 5/03\>Laboratory Instructor \& Grader for PHY110A, University of Cape Town,\\
\>South Africa \\
\end{tabbing}

\newpage
\begin{description}
\item[\bf Research highlights:]\
\begin{itemize}
\item Fellow of the APS Division of Nuclear Physics (September 2017)
\item Co-convenor of ATLAS heavy ion physics group (2008-2011, 2016-2018)
\item Co-project leader of ATLAS Zero Degree Calorimeter (2015, 2018-)
\item Several reviews and journal volumes on heavy ion physics ``Glauber modeling in high energy nuclear collisions'' M.L.Miller, K.Reygers, S.J.Sanders and P.Steinberg, Ann. Rev. Nucl. Part. Sci. 57 (2007) - 1801 citations on Google Scholar, 1116 citations on Inspire.
\item ``Observation of a Centrality-Dependent Dijet Asymmetry in Lead-Lead Collisions at $\snn276$ with the ATLAS Detector at the LHC'', Phys. Rev. Lett. 105, 252303 (2010) - 745 citations on Inspire.
\item co-chair of Initial Stages 2019, at Columbia University
\item Co-author of PHOBOS Glauber Monte Carlo, code still used widely in field and under constant development
\item Speaker at many cross-disciplinary workshops, including heavy ion physics.
\end{itemize}
\end{description}

\newpage

\begin{description}

\item[\bf Selected Publications and conference proceedings:]\
\begin{itemize}
\item ``Measurement of light-by-light scattering and search for axion-like particles with 2.2 nb$^{-1}$ of Pb+Pb data with the ATLAS detector'', submitted to JHEP
\item ``Z boson production in Pb+Pb collisions at 5.02 TeV measured by the ATLAS experiment'', Phys. Lett. B 802 (2020) 135262.
\item ``Measurement of W boson production in the muon channel in Pb+Pb collisions at $\sqrt{s_{NN}}=5.02$ TeV'', Eur. Phys. J. C 79 (2019) 935
\item ``Observation of light-by-light scattering in ultraperipheral Pb+Pb collisions with the ATLAS detector'', Phys. Rev. Lett. 123, 052001 (2019)
\item ``Measurement of photon-jet transverse momentum correlations in 5.02 TeV Pb + Pb and pp collisions with ATLAS'', ATLAS Experiment, Phys. Lett. B 789 (2019) 167.
\item ``Observation of centrality-dependent acoplanarity for muon pairs produced via two-photon scattering in Pb+Pb collisions at $\sqrt{s_{NN}}=5.02$ TeV with the ATLAS detector'', Phys. Rev. Lett. 121 (2018) 212301
\item ``Evidence for light-by-light scattering in heavy-ion collisions with the ATLAS detector at the LHC'', Nature Physics 13 (2017) 852
\item ``Femtoscopy with identified charged pions in proton-lead collisions at $\sqrt{s_{NN}}$=5.02 TeV with ATLAS'', Phys. Rev. C 96 (2017) 064908
\item ``Photo-nuclear dijet production in ultra-peripheral Pb+Pb collisions'', ATLAS-CONF-2017-011 (2017)
\item ``Centrality, rapidity and transverse momentum dependence of isolated prompt photon production in lead-lead collisions at $\snn$=2.76 TeV measured with the ATLAS detector'', Phys. Rev. C 93 (2016) 034914.
\item ``Measurement of the centrality dependence of the charged-particle pseudorapidity distribution in proton-lead collisions at sqrt(sNN)=5.02 TeV with the ATLAS detector'', European Physical Journal C, April 2016, 76:199
\item ``$Z$ boson production in $p+$Pb collisions at $\sqrt{s_{NN}}=5.02$ TeV measured with the ATLAS detector'', Phys Rev C92 044915 (2015).
\item ``Measurement of the dependence of transverse energy production at large rapidity on the hard scattering kinematics of proton-proton collisions at $\snn$=2.76 TeV with ATLAS'', Phys. Lett. B 756 (2016) 10-28.
\item ``Measurement of high-mass dimuon pairs from ultraperipheral lead-lead collisions at $\sqrt{s_{\mathrm{NN}}}=5.02$ TeV with the ATLAS detector at the LHC'', ATLAS-CONF-2016-025 (2016)
\item ``Observation of Associated Near-side and Away-side Long-range Correlations in $\snn$=5.02 TeV Proton-lead Collisions with the ATLAS Detector``, Phys.Rev.Lett. 110 182302 (2013).
\item ``Measurement of the pseudorapidity and transverse momentum dependence of the elliptic flow of charged particles in lead-lead collisions at $\snn$ = 2.76 TeV with the ATLAS detector'', Phys.Lett. B707 (2012) 330-348.
\item  ``Measurement of the centrality dependence of the charged particle pseudorapidity distribution in lead-lead collisions at $\snn$=2.76 TeV with the ATLAS detector'', arXiv:1108.6027, submitted to Phys. Lett. B.  Phys.Lett. B710 (2012) 363-382.
\item  ``Measurement of elliptic flow and higher-order flow coefficients with the ATLAS detector in $\snn$ = 2.76 TeV TeV Pb+Pb collisions'', ATLAS-CONF-2011-074 (2011).
\item ``Centrality dependence of Jet Yields and Jet Fragmentation in Lead-Lead Collisions at $\snn$ = 2.76 TeV with the ATLAS detector at the LHC'', ATLAS-CONF-2011-075 (2011).
\item ``Measurements of W Boson Yields in Pb+Pb at 2.76 TeV/nucleon via single muons with the ATLAS detector'', ATLAS-CONF-2011-078 (2011).
\item ``Measurement of the centrality dependence of charged particle spectra and $R_{CP}$ in lead-lead collisions at $\snn$ = 2.76 TeV with the ATLAS detector at the LHC'', ATLAS-CONF-2011-079 (2011).
\item ``Measurement of the centrality dependence of $J/\psi$ yields and observation of Z production in lead-lead collisions with the ATLAS detector at the LHC'', Physics Letters B697, 294-312 (2011).
\item ``Observation of a Centrality-Dependent Dijet Asymmetry in Lead-Lead Collisions at $\snn276$ with the ATLAS Detector at the LHC'', Phys. Rev. Lett. 105, 252303 (2010).
\item ``Phobos results on charged particle multiplicity and pseudorapidity distributions in Au+Au, Cu+Cu, d+Au, and p+p collisions at ultra-relativistic energies'', B. Alver, et al (PHOBOS Collaboration), Phys. Rev. C 83, 024913 (2011).
\item ``Event-by-event fluctuations of azimuthal particle anisotropy in Au+Au collisions at $\snn$ = 200 GeV'', B. Alver, et al (PHOBOS Collaboration), Phys. Rev. Lett. 104, 142301 (2010).
\item ``High transverse momentum triggered correlations over a large pseudorapidity acceptance in   Au+Au collisions at $\snn$ = 200 GeV'', B. Alver, et al (PHOBOS Collaboration), Phys. Rev. Lett. 104, 062301 (2010).
\item ``System size dependence of cluster properties from two-particle angular correlations in Cu+Cu and Au+Au collisions at $\snn$ = 200 GeV'', B. Alver, et al (PHOBOS Collaboration), Phys. Rev. C81, 024904 (2010).
\item ``Quantitative and conceptual considerations for extracting the Knudsen number in heavy ion collisions'', J. Nagle, P. Steinberg and W.A. Zajc, Phys. Rev. C 81, 024901 (2010).
\item ``Soft Physics from RHIC to LHC'', P. Steinberg, Nucl.Phys. A827, 128C-136C (2009).
\item ``System size, energy and centrality dependence of pseudorapidity distributions of charged particles in relativistic heavy ion collisions'', B. Alver, et al (PHOBOS Collaboration), Phys. Rev. Lett. 102, 142301 (2009).
\item ``Quasi-Particle Degrees of Freedom versus the Perfect Fluid as Descriptors of the Quark-Gluon Plasma'', L. A. Linden Levy, J. L. Nagle, C. Rosen (U. Colorado), P. Steinberg, Phys. Rev. C 78, 044905 (2008).
\item ``The PHOBOS Glauber Monte Carlo'', B. Alver, M. Baker, C. Loizides, P. Steinberg, (arxiv:0805.4411, code on HepForge) (2008).
\item ``The Importance of Correlations and Fluctuations on the Initial Source Eccentricity in High-Energy Nucleus-Nucleus Collisions'', B. Alver, et al (PHOBOS Collaboration), Phys. Rev. C77, 014906 (2008).
\item ``Consequences of Early Thermalization at Low and High $p_T$'', P. Steinberg, Proceedings for ``High $p_T$ physics at LHC'', Jyvaskyla, Finland, March 23-27, 2007, PoS(LHC07)033 (2007).
\item ``Heavy ion physics at the LHC with the ATLAS detector'', P. Steinberg for the ATLAS Collaboration, J. Phys. G34:S527-534 (2007).
\item ``Inclusive Pseudorapidity Distributions in p(d)+A Collisions Modeled With Shifted Rapidity Distributions'', P. Steinberg, Submitted to Physics Letters B (nucl-ex/0703002)
\item ``Hotter, Denser, Faster, Smaller...and Nearly-Perfect: What's the matter at RHIC?'', P. Steinberg, APS Topical Group on Hadronic Physics, Nashville, Tennesse, 22-24 Oct 2006, J. Phys.: Conf. Ser. 69 012032 (2007).
\item  ``Glauber modeling in high energy nuclear collisions'' M.L.Miller, K.Reygers, S.J.Sanders and P.Steinberg, Ann. Rev. Nucl. Part. Sci. 57 (2007).
\item ``Vertex Reconstruction Using a Single Layer Silicon Detector'', E. Garcia et al, Nucl. Instrum. Meth. A570:536-542 (2007).
\item ``System size, energy, pseudorapidity, and centrality dependence of elliptic flow'', B.B. Back et al, Phys.Rev.Lett.98:242302 (2007).
\item ``Cluster properties from two-particle angular correlations in p+p collisions at $\sqrt{s}$ = 200 and 410 GeV'', B. Alver et al, Phys. Rev. C75, 054913 (2007).
\item ``Entropy Production at High Energy and mu(B)'', P.Steinberg, proceedings for ``Critical Point and Onset of Deconfinement'', Florence, Italy, 3-6 Jul 2006, PoS CPOD2006:036 (2006).
\item  ``Charged Particle Pseudorapidity Distributions in Au+Au collisions at $\snn$ = 62.4 GeV'', B.B. Back, et al, Phys. Rev. C74, 021901(R) (2006).
\item  ``Centrality and energy dependence of charged-particle multiplicities in heavy ion collisions in the context of elementary reactions'', B.B. Back et al, Phys.Rev. C74, 021902 (2006).
\item ``Forward-backward multiplicity correlations in $\snn$ =200 GeV Au+Au collisions'', B.B. Back, et al, Phys.Rev.C74:011901 (2006).
\item ``System size and centrality dependence of charged hadron transverse momentum spectra in Au+Au and Cu+Cu collisions at $\snn$=62.4 and 200 GeV'', Phys. Rev. Lett. 96, 212301 (2006).
\item ``The Origin of the Difference Between Multiplicities in e+e- annihilation and heavy ion collisions'', J. Cleymans, M. Stankiewicz, P. Steinberg, S. Wheaton (submitted to Physics Letters B, nucl-th/0506027) (2005).
\item ``Scaling of Charged Particle Production in d+Au Collisions at $\snn$=200 GeV'', B.B. Back, et al (PHOBOS Collaboration), Phys. Rev. C72, 031901(R) (2005).
\item ``The PHOBOS Perspective on Discoveries at RHIC'', B.B. Back, et al (PHOBOS Collaboration), Nucl. Phys. A757, 28 (2005).
\item ``Centrality dependence of charged hadron transverse momentum spectra in Au+Au collisions from $\snn$ = 62.4 to 200 GeV'', B.B. Back, et al (PHOBOS Collaboration), Phys. Rev. Lett.  94, 082304 (2005).
\item ``Pseudorapidity dependence of charged hadron transverse momentum spectra in d+Au collisions at $\snn$=200 GeV'', B.B. Back, et al (PHOBOS Collaboration), Phys. Rev. C70, 061901(R) (2004).
\item ``Collision Geometry Scaling of Au+Au pseudorapidity density from $\snn$ = 19.6 to 200 GeV'', B.B. Back, et al (PHOBOS Collaboration), Phys. Rev. C70, 021902(R) (2004).
\item ``Particle production at very low transverse momenta in Au+Au collisions at $\snn$=200 GeV'', B.B. Back, et al (PHOBOS Collaboration), Phys. Rev. C70, 051901(R) (2004).
\item ``Pseudorapidity Distribution of Charged Particles in d+Au collisions at $\snn$=200 GeV'', B.B. Back, et al (PHOBOS Collaboration), Phys. Rev. Lett. 93, 082301 (2004).
\item ``Centrality Dependence of the Charged Hadron Transverse Momentum Spectra in d+Au Collisions at $\snn$ =200 GeV'', B.B. Back, et al (PHOBOS Collaboration), Phys. Rev. Lett. 91, 072302 (2003).
\item ``Charged hadron transverse momentum distributions in Au+Au collisions at $\snn$= 200 GeV'', B.B. Back, et al (PHOBOS Collaboration), Phys. Lett. B578, 297 (2004).
\item ``Significance of the fragmentation region in ultrarelativistic heavy ion collisions'', B.B. Back, et al (PHOBOS Collaboration), Phys. Rev. Lett. 91, 052303 (2003).
\item  ``Centrality Dependence of the Charged Particle Multiplicity near Mid-Rapidity in  Au+Au Collisions at $\snn$ = 130 and 200 GeV'', B.B. Back, et al (PHOBOS Collaboration), Phys. Rev. C65, 061901(R) (2002)
\item ``Energy dependence of particle multiplicities near mid-rapidity in central Au+Au collisions'', B.B. Back, et al (PHOBOS Collaboration), Phys. Rev. Lett. 88, 22302 (2002).
\item X ``Centrality Dependence of Charged Particle Multiplicity at Midrapidity in Au+Au Collisions at $\snn$ = 130 GeV'', B.B. Back, et al (PHOBOS Collaboration), Phys. Rev. C65, 31901(R) (2002).
\item ``Charged-particle pseudorapidity density distributions from Au+Au collisions at $\snn$ = 130 GeV'', B.B. Back, et al (PHOBOS Collaboration), Phys. Rev. Lett. 87, 102303 (2001).
\item  ``Charged particle multiplicity near mid-rapidity in central Au+Au collisions at $\snn$ = 56 and 130 AGeV'', B.B. Back, et al (PHOBOS Collaboration), Phys. Rev. Lett. 85, 3100 (2000).
\item ``Search for disoriented chiral condensates in 158-GeV/A Pb + Pb collisions'', M.M. Aggarwal, et al (WA98 Collaboration), Phys.Lett. B420 169-179 (1998).
\end{itemize}

%\item[{\bf \underline{Invited Talks}:}]\

\item[\bf Talks:]\
\begin{itemize}
\item ``Ultraperipheral collisions'', invited plneary talk at Quark Matter 2019, November 4-9, 2019 Wuhan, China.
\item ``Collectivity in hadronic collisions'', invited talk at workshop ``Hydrodynamics across the scales'', University of Chicago, April 27-28, 2019.
\item ``Photon-photon collisions at RHIC and the LHC'', plenary talk at the GHP2019 workshop, Denver, CO, April 10-12, 2019.
\item ``Physics with the ATLAS ZDC,'' talk at Forward Physics And Instrumentation From Colliders To Cosmic Rays, Stony Brook University, October 2018.
\item ``Electromagnetic processes with Quasireal photons in Pb+Pb collisions:  QED, QCD, and the QGP'', invited parallel talk at EIC users meeting, Catholic University, Washington, DC August 2018.
\item ``Jets in small systems'', invited talk at Workshop on ``Probing Quark-Gluon Matter with Jets'' 23-27 July 2018, Brookhaven National Laboratory.
\item ``Electromagnetic processes with Quasireal photons in Pb+Pb collisions:  QED, QCD, and the QGP'', invited parallel talk at Quark Matter 2018, Venice, May 2018.
\item ``Electromagnetic processes in ultraperipheral Pb+Pb collisions with ATLAS'', Initial Stages 2017 (IS2017), September 2017, 2017.
\item ``A Tale of Collectivity in Collisions of Ions, Large and Small,'' Talk/Seminar presented at Oxford workshop ``Canterbury Tales of Hot QCD'', July 2017.
\item ``Photon-jet correlations in sqrt($s_{NN}$)=5.02 TeV pp and Pb+Pb collisions with ATLAS at the LHC'', invited parallel talk at Quark Matter 2017, Chicago, Illinois, February 2017.
\item ``How small is too small?'', invited talk for workshop ``ULtra-RelatIvistiCH HEavy IoNZ'', CERN, Geneva, Switzerland, July 2016.
\item ``Measurement of exclusive dimuon production in ultra-peripheral collisions with ATLAS at the LHC'', invited talk for the workshop ``Proton and Photon-induced nuclear collisions at the LHC'', CERN, Geneva, Switzerland, July 2016.
\item ``Measurement of exclusive dimuon production in ultra-peripheral collisions with ATLAS at the LHC'', invited parallel talk at Initial Stages 2016, Lisbon, Portugal, May 2016.
\item ``Measurement of the dependence of transverse energy production at large pseudorapidity on the hard scattering kinematics of proton-proton collisions at $\snn$= 2.76 TeV'', invited parallel talk at Hard Probes 2015, Montreal Canada, July 2015.
\item ``Jet measurements in p+Pb and Pb+Pb collisions with ATLAS'', invited parallel talk at Initial Stages 2014, Napa, CA, December 2014.
\item ``Centrality, rapidity and transverse momentum dependence of isolated prompt photon production in lead-lead collisions at $\snn$=2.76 TeV measured with the ATLAS detector'', invited parallel talk at Quark Matter 2014, Darmstadt, Germany, May 2014.
\item ``What have we learned about the quark-gluon plasma, using hard probes with the ATLAS experiment at the LHC'', invited plenary talk at Hard Probes 2013, Cape Town, South Africa, November 2013.
\item ``Photons and electroweak probes in ATLAS'', invited plenary talk for Quark Matter 2012, Washington, DC, August 2012.
\item ``Recent Heavy Ion Results with the ATLAS Detector at the LHC'', invited talk at Division of Nuclear Physics meeting, East Lansing, MI, October 29, 2011.
\item ``Heavy Ion Physics with the ATLAS Detector at the LHC'', talk at the Tomography/Holography 2011 workshop at Columbia University, October 20, 2011.
\item ``Recent Heavy Ion Results with the ATLAS Detector at the LHC'', invited parallel talk at Division of Particle and Fields meeting, Brown University, Providence, RI, August 12, 2011.
\item ``Suppression of high $p_{T}$ particles with the ATLAS Detector at the LHC'', talk given at Symposium on Jet Physics at RHIC and the LHC, Hangzhou, China, July 21, 2011.
\item ``Running RHIC Beyond 2017'', talk at RHIC Long Range Planning Workshop, BNL, June 22, 2011.
\item ``Recent Heavy Ion Results with the ATLAS Detector at the LHC'', plenary talk at Quark Matter 2011, Annecy, France, May 23, 2011.
\item ``Hard Probes Measured with the ATLAS Detector at the LHC'', talk at the LPC workshop ``HI @ LHC'', CERN, Geneva, March 4, 2011.
\item ``Heavy Ion Physics with the ATLAS Detector at the LHC'', invited talk given at Les Rencontres de Physique de la Vall\'ee d'Aoste 2011, March 1, 2011.
\item ``The Present and Future RHIC Program at Brookhaven National Laboratory'', invited talk given at the 13th SAC Seminar ``New Perspectives of High Energy Physics'', Novosibirsk, Siberia, September 3, 2010.
\item ``Preparations for the ATLAS Heavy Ion Physics Program'', parallel talk at INPC 2010, Vancouver, Canada, July 8, 2010.
\item ``Study of the Perfect Liquid at RHIC'', invited symposium talk at ``Fermions at Unitarity: Gravity, the Quark-Gluon Plasma, and Ultra-Cold Atoms'', APS March Meeting 2010, March 17, 2010. 
\item ``Apples with applies: comparing initial states in theory \& experiment'', talk at TECHQM/CATHIE Workshop, December 14, 2009.

\item ``The ATLAS Heavy Ion Program'', talk at SA-CERN launch, iThemba Labs, Stellenbosch, South Africa, December 15, 2008.
\item ``Lectures on Heavy Ion Physics'', talk at ``Applications of AdS/CFT'', sti$\alpha$s, Stellenbosch, South Africa, December 10, 2008.
\item ``Soft Physics from RHIC to the LHC'', invited plenary talk at PANIC 2008, Eilat, Israel, November 13, 2008.
\item ``Global Variables in Heavy Ion Collisions at the LHC with the ATLAS Detector'', parallel talk given at Quark Matter 2008, Jaipur, India, February 9, 2008.
\item ``(Unintended) Consequences of the Glauber Initial State'', talk given at the conference ``Early Time Dynamics in Heavy Ion Collisions'', McGill University, Montreal, Canada, July 17, 2007.
\item ``Introduction to the Study of Heavy Ion Collisions'', three lectures given at the National Nuclear Physics Summer School, Florida State University, Tallahassee, Florida, July 9-11, 2007.
\item ``The Tao of PHOBOS'', plenary talk given at the RHIC/AGS Users Meeting, Brookhaven, June 18, 2007.
\item ``Consequences of Early Thermalization at Low and High $p_T$'', talk given at the workshop ``High $p_T$ Physics at the LHC'', Jyvaskyla, Finland, March 2007.
\item ``Scientific Status of the RHIC Heavy Ion Program'', talk given at the Nuclear Physics Long Range Planning workshop ``Phases of QCD Matter'', Rutgers University, January 12-14, 2007.
\item ``Heavy Ion Physics at the LHC with ATLAS'', plenary talk given at Quark Matter 2006, Shanghai, China, November 19, 2006.
\item ``Hotter, Denser, Faster, Smaller...and Nearly-Perfect: What's the matter at RHIC?'', Invited talk at Group on Hadron Physics 2006, Nashville, October 22, 2006.
\item ``Entropy at High E and $\mu_B$'', talk given at the workshop ``Critical Point and the Onset of Deconfinement (CPOD2006)'', Florence, Italy, 5 July 2006.
\item ``Workshops Summary'', plenary talk given at the RHIC/AGS Users' Meeting, June 5, 2006.
\item ``Multiplicity Systematics at high E and $\mu_B$'', talk given at the workshop ``From High Energy to High $\mu_B$'' at the RHIC/AGS Users' Meeting, June 5, 2006.
\item ``PHENIX Capabilities for the Low Energy RHIC Run'', talk given at Workshop on the Critical Point at RHIC, March 9, 2006.
\item ``Hotter, Denser, Faster, Smaller...and Nearly-Perfect: What's the matter at RHIC?'', Physics Colloquium at The Ohio State University, Columbus, OH, March 7, 2006.
\item ``Hotter, Denser, Faster, Smaller...and Nearly-Perfect: What's the matter at RHIC?'' 410th BNL Lecture, December 21, 2005.
\item ``(Nearly) Perfect Fluids and Perturbative Probes: a Primer on RHIC Physics'', Lecture given at the 2005 International School on Subatomic Physics, Erice, Sicily, August 29-September 7, 2005.
\item ``Forward-Backward Multiplicity Correlations Corrleations in Au+Au'', parallel talk given at Quark Matter 2005, Budapest, Hungary, August 2005.
\item ``The Thermochemistry and Hydrodynamics of the Strong Interaction: Results from RHIC'', talk given at the Gordon Research Conference, Bates College, Lewiston, Maine, July 12, 2005.
\item ``Some RHIC Advice for LHC Day-1 Physics'' Talk given at ATLAS Week, CERN, Geneva February 14-18, 2005.
\item ``Particle Multiplicities in Heavy Ion Collisions'' Invited talk at Group on Hadron Physics 2004 (GHP2004), Fermilab, Batavia, Illinois, October 24-26, 2004.
\item ``Stranger in a Strange Land (Conference Summary)'' Invited talk at Strangeness in Quark Matter 2004 (SQM2004), Cape Town, South Africa, Sept 15-20, 2004.
\item ``Thoughts on Heavy Quark Production'' Invited talk at Hot Quarks 2004 (HQ2004), Taos, New Mexico, July 18-24, 2004.
\item ``Bulk Dynamics in Heavy Ion Collisions'' Invited talk at INPC 2004, Goteborg, Sweden, June 28 - July 2, 2004.
\item ``Landau Hydrodynamics and RHIC Phenomenology'' presented at 20th Winter Workshop on Nuclear Dynamics, Jamaica, March 14-21, 2004.
\item ``The Landscape of Particle Production: Recent Results from PHOBOS'' plenary talk presented at Quark Matter 2004, Oakland, CA, January 11-18, 2004.
\item ``High $p_T$ Physics at RHIC: Glauber Summary'', presented at the RIKEN workshop "High-$p_T$ Physics at RHIC", Brookhaven National Laboratory, December 2-6, 2003.
\item ``Landau Hydrodynamics \& RHIC Phenomenology'', Invited talk presented at the RIKEN/\\BNL Workshop ``Collective flow and QGP properties'', 17-19 November 2003.
\item ``Status of Parton Saturation at RHIC'', Invited talk presented at Forward Physics at RHIC Workshop, Brookhaven National Lab, 9 October 2003.
\item ``Status of Parton Saturation at RHIC'', Invited talk presented at ISMD2003, Krakow, Poland, 5-11 September 2003.
\item ``Dynamics of Soft Particle Production in Heavy Ion Collisions'', Invited talk presented at CIPANP2003, New York, NY, 19-24 May 2003.
\item ``Universal Aspects of Particle Production in Heavy Ion Collisions'', Nuclear and Particle Physics Colloquium presented at Massachusetts Institute of Technology, Cambridge, MA, February 3, 2003.
\item ``Universal Aspects of Particle Production in Heavy Ion Collisions'', Colloquium presented at Schonland Research Centre for Nuclear Sciences, University of the Witwatersrand, Johannesburg, South Africa, December 10, 2002.
\item ``Relativistic Heavy Ion Phyics: Results from AGS to RHIC''.  Colloquium presented at the University of Stellenbosch, South Africa, November 8, 2002.
\item ``Relativistic Heavy Ion Phyics: Results from AGS to RHIC''.  Colloquium presented at the University of Cape Town, South Africa, August 14, 2002.
\item ``Universal Behavior of Charged Particle Production in Heavy Ion Collisions''.  Parallel session at ICHEP 2002, Amsterdam, The Netherlands, July 24-31, 2002.
\item ``Universal Behavior of Charged Particle Production in Heavy Ion Collisions''.  Parallel session at Quark Matter 2002, Nantes, France, July 18-24, 2002.
\item ``Relativistic Heavy Ion Collisions: Recent Results''.  Invited talk presented at Physics in Collision XXII, Stanford, CA, June 20-22, 2002.
\item ``Everything Counts: Multiplicity Measurements in High Energy Collisions''.  Invited talk presented at the ITP Workshop ``QCD in the RHIC Era'', UC Santa Barbara, April 8-12, 2002.
\item ``Counting on QCD: Multiplicity Measurements in High Energy Collisions''.  Physics Department Colloquium at Brookhaven National Laboratory, December 4, 2001.
\item ``RHIC: QCD Matter in the Laboratory''.  Colloquium given at George Washington University, Washington, D.C., November 15, 2001.
\item ``Recent Results from PHOBOS @ RHIC''.  Invited talk presented at the International Symposium on Multiparticle Dynamics, Datong, China, September 1-7, 2001.
\item ``Energy and Centrality Dependence of Global Observables in Heavy Ion Collisions''.  Invited talk presented at the national meeting of the American Chemical Society, Chicago, August 25-29, 2001.
\item ``A Tale of Two Glauber Calculations: Monte Carlo and Optical Limit Approaches''.  Invited talk given at the Glauber2001 Workshop at Brookhaven National Laboratory, July 19, 2001.
\item ``Elliptic flow and Particle Ratios with PHOBOS''.  Invited talk at RHIC/INT Workshop, Lawrence Berkeley National Laboratory, May 31 - June 2, 2001.
\item ``RHIC Rapporteur II: Global and Flow Observables''.  Invited talk at Quark Matter 2001, Stony Brook, January 14-20, 2001.
\item ``Results from the PHOBOS Experiment at RHIC''.  Invited talk at the Annual Fall Meeting of the Division of Nuclear Physics (DNP) of the American Physical Society (APS), Williamsburg, Virginia, October 4-7, 2000.
%\item ``ROOT in the PHOBOS Online System''.  Talk given at the ``2nd ROOT Workshop'', CERN, Geneva, February 3-5, 2000.
%\item ``Multiparticle Bose-Einstein Correlations In Heavy Ion Collision''.  Talk given at the ``International Symposium on Multiparticle Dynamics'', Providence, RI, August 1999.
%\item ``Data Collection Modules and an ATM-based Event Builder for the PHENIX Experiment at RHIC''.  Talk given at the IEEE ``Real Time '99'', Sante Fe, New Mexico, June 13-18, 1999.
%\item ``Disoriented Chiral Condensates: recent results''.  Talk given at the APS Centennial Meeting, Atlanta, Georgia, March 21-25, 1999.
%\item ``Development of an ATM-based Event Builder for the PHENIX Experiment at RHIC''.  Talk given at ``Applications of ATM in High Energy Physics'', Paris, September 21-22, 1998.
\item ``Development of an ATM-based Event Builder for the PHENIX Experiment at RHIC''.  Talk given at CHEP98, Chicago, August 31 - September 4, 1988.
\item ``Searching for DCCs with the WA98 Experiment''.  Invited talk at the ``Nuclear Chemistry Gordon Research Conference'', New London, NH, June 17, 1998.
\item ``Search for Disoriented Chiral Condensates in 158 Pb+Pb collisions''.  Invited talk at the ``International Symposium on Multiparticle Dynamics '97'', Frascati, Italy, September 11, 1997.
%\item ``Searching for Disoriented Chiral Condensates''.  Talk given at the ``RHIC/INT Winter Workshop'', Lawrence Berkeley Laboratory, February 21-22, 1997.
%\item ``Search for Disoriented Chiral Condensates in 158 Pb+Pb collisions''.  Invited talk at ``Phase Transitions '97'', Niels Bohr Institute, Copenhagen, Denmark, November 25-30, 1997.
%\item ``Charged Multplicity Measurements in WA98''.  Invited talk at the ``International Workshop on Disoriented Chiral Condensates'', Trento, Italy, October 21-25, 1996.
\end{itemize}

\item[Invited Colloquia \& Seminars:]\
\begin{itemize}

\item ``Heavy Ion Physics with ATLAS at the LHC'', Colloqiua presented at DESY Hamburg and DESY Zeuthen, Germany, July 2016
\item ``Two particle correlations in proton-lead collisions at the LHC'', Colloqiua presented at DESY Zeuthen, Germany, June 2013
\item ``Heavy ion physics with ATLAS'', Seminar presented at University of Chicago Physics Department, November 2012
\item ``Heavy ion physics with ATLAS'', Seminar presented at New York University Physics Department, November 2012
\item ``Electroweak probes with ATLAS'', Seminar presented at LBL, February 2012
\item ``Observation of a centrality-dependent dijet asymmetry in lead-lead collisions at $\snn276$ with the ATLAS Detector at the LHC,'' Brookhaven Physics Department Colloquium, December 14, 2010.
\item ``Study of the Perfect Liquid at RHIC'', Seminar given at the University of Virginia Physics Department, April 9, 2010.
\item ``Puzzles in Soft Physics: from RHIC to the LHC'', Seminar given at Perimeter Institute, Waterloo, Ontario, October 9, 2009.
\item ``A Large Range of 2-particle Corrrelations Measureents with PHOBOS'', Brookhaven Nuclear Physics Seminar, February 3, 2009.
\item ``Entropy at high energy and $\mu_B$'', seminar at Columbia University, January 25, 2009.
\item ``Introduction to Heavy Ion Collisions: Three Lectures'', P.Steinberg, Presented at the National Nuclear Physics Summer School, Florida State University, 9-11 July 2007.
\item ``Hotter, Denser, Faster, Smaller...and Nearly Perfect: What's the matter at RHIC'', Colloquium at U.C. Riverside, May 17, 2007.
\item ``Hotter, Denser, Faster, Smaller...and Nearly Perfect: What's the matter at RHIC'', Colloquium at Ohio State University, March 6, 2006.
\item ``Hotter, Denser, Faster, Smaller...and Nearly Perfect: What's the matter at RHIC'', Brookhaven Lecture, December 22, 2005.
\item ``The Thermochemistry and Hydrodynamics of the Strong Interation: Results from RHIC (RHIC for Chemists)'', Brookhaven Chemistry Department Colloquium, May 20, 2005.
\item ``The Landscape of the Strong Interaction: Results from PHOBOS'', Seminar at Yale University, 19 February 2004.
\item ``Universal Aspects of Particle Production in Heavy Ion Collisions'', Seminar presented at Triangle Nuclear Theory Seminar, Duke University, Durham, NC, January 20, 2003.
\item ``Systematics of Charged Particle Production at RHIC with the PHOBOS Detector''.  Seminar given at Lawrence Berkeley Laboratory, November 6, 2001.
\item ``Isospin Fluctuations in Heavy Ion Collisions''.  Invited Seminar given at MIT, Cambridge, MA, March 1999
\item ``Search for DCCs with WA98 at the CERN SPS''.  Invited Seminar given at Yale University, New Haven, CT, October 14, 1997.
\item ``Search for Disoriented Chiral Condensates in 158 Pb+Pb collisions''.  Invited seminar at the University of Lund, Sweden, December 2, 1996. 
\end{itemize}

\item[Outreach and national media:]\
\begin{itemize}
\item Presentation of RHIC and LHC physics in ``People Pie Pool'' at Performa 2017, New York City.
\item ``What black holes teach about strongly coupled particles'', C. Johnson and P. Steinberg, in May 2010 issue of Physics Today magazine (based on 2009 AAAS symposium) \url{http://physicstoday.org/resource/1/phtoad/v63/i5}.  Translated into Japanese for Parity Magazine in 2011. 
\item ``Creating the perfect liquid in heavy-ion collisions'', B. Jacak and P. Steinberg, in May 2010 issue of Physics Today magazine (based on 2009 AAAS symposium) \url{http://physicstoday.org/resource/1/phtoad/v63/i5}.  Translated into Japanese for Parity Magazine in 2011. 
\item Co-organizer (with W.A. Zajc) of ``The Quest for the Perfect Liquid'', symposium at AAAS2009, Chicago, Illinois, February 15, 2009.
\item Blogger for InterAction's ``Quantum Diaries'', January 1, 2005 - December 31, 2005, \url{http://qd.typepad.com/5}
\item Blogger for US-LHC blogs (now part of Quantum Diaries), \url{http://www.quantumdiaries.org/author/peter-steinberg/}
\item Private blogger for ``Entropy bound'', \url{http://entropybound.blogspot.com}
\item ``Plot Device of Mass Destruction: Antimatter's True Story'' for Discovery Space website, April 28, 2009, \url{http://dsc.discovery.com/space/my-take/anti-matter-angels-and-demons.html}
\item ``No mere cog: Blogging the LHC'', essay for Symmetry Magazine, December 2007, \url{http://www.symmetrymagazine.org/cms/?pid=1000573}
\item ``Why I am a Physicist'', guest post for Backreaction, February 18, 2007, \url{http://backreaction.blogspot.com/2007/02/guest-post-peter-steinberg.html}
\item ``What's in a Proton?'' (excerpt from 2005 Brookhaven Lecture), Brookhaven National Laboratory YouTube channel, \url{http://www.youtube.com/watch?v=MQL0l0lyKOQ}
\item ``Quark-Gluon Plasma: A New State of Matter'' (excerpt from 2005 Brookhaven Lecture), Brookhaven National Laboratory YouTube channel, \url{http://www.youtube.com/watch?v=xBYKWEH4HfI}
\item ``Colliding Nuclei at High Energy'' (excerpt from 2005 Brookhaven Lecture), Brookhaven National Laboratory YouTube channel, \url{http://www.youtube.com/watch?v=Vyq_AYWctSo}
\end{itemize}

\end{description}

\end{document}





